Monte Carlo simulation of monetary transactions: \\ \normalsize{A simple model for wealth distribution} \\ \hrulefill\small{ FYS3150: Computational Physics }\hrulefill

### 2016-12-09 Project5/article/article.tex
Results done (for now)

@@

\begin{figure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\textwidth]{../figures/5ac/5cLOGLOG_N500_varSavings.pdf}
  \caption{}
  \label{fig:logdistribution}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../figures/5ac/omega.pdf}
  \caption{}
  \label{fig:straightline}
\end{subfigure}
\caption{Logarithmic plot wealth distribution from figure \ref{fig:distribution} (right), and the logarithm of the Gibbs measure (equation \ref{eq:gibbs}) of every data point (right).}
\label{fig:logplot}
\end{figure}

@@

%% Problem d.
\begin{figure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5d/5d_0-var-0.pdf}
	\caption{}
	\label{fig:neighbour1}
\end{subfigure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5d/5d_05-var-0.pdf}
	\caption{}
	\label{fig:neighbour2}
\end{subfigure}
\caption{Effect of neighbour-only interaction}
\end{figure}

\begin{figure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5d/5d_0-var-0-PARETO.pdf}
	\caption{}
	\label{fig:neighbourpareto1}
\end{subfigure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5d/5d_0-var-0-POWERLOG.pdf}
	\caption{}
	\label{fig:neighourpareto2}
\end{subfigure}
\caption{Effect of neighbour-only interaction}
\end{figure}

@@

\section{Parametrization from Patriarcal et al.}
\label{app:partriarca}
A corresponding exact solution of an income distributions for a generic value of $\lambda$ with $0<\lambda<1$ is provided in Patriarca et al.\cite{Patriarca}. Fir one employs the reduced variable
\begin{equation}
x = \frac{m}{\ev{m}}
\end{equation}
the agent money in units of average money $\ev{m}$ and the parameter
\begin{equation}
n(\lambda) = 1 + \frac{3\lambda}{1-\lambda}.
\end{equation}
The money distributions, for arbitrary values of $\lambda$, are well fitted by the function
\begin{equation}
P_n(x) = a_nx^{n-1}e^{-nx}
\end{equation}
where $a_n$ is a normalization factor shown to be
\begin{equation}
a_n = \frac{n^n}{\Gamma(n)}
\end{equation}
\end{appendices}

>>>>

\begin{figure}
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\textwidth]{../figures/5ac/5cLOGLOG_N500_varSavings.pdf}
  \caption{}
  \label{fig:logdistribution}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../figures/5ac/omega.pdf}
  \caption{}
  \label{fig:straightline}
\end{subfigure}
\caption{Logarithmic plot of wealth distribution from figure \ref{fig:distribution} \ref{fig:logdistribution}), and the logarithm of the Gibbs measure (equation \ref{eq:gibbs}) of every data point (\ref{fig:straightline}).}
\label{fig:logplot}
\end{figure}

@@

@@

%% Problem d.

The effect of ``nearest neighbhour'' interactions are summarized in figures \ref{fig:neighbour} and \ref{fig:neighbourpareto}. Figure \ref{fig:neighbour} shows logarithmic plots of simulations for different values of $\alpha$ from equation \ref{eq:rigidprob}. The parameter for previous transactions $gamma$ is set to zero for now. The only difference between the subfigures in figure \ref{fig:neighbour} is that figure \ref{fig:neighbour1} is for $\lambda=0$ and figure \ref{fig:neighbour2} is for $\lambda=0.5$, colloquially with and without saving respectively. Figure \ref{fig:neighbour} shows similar results to that of Goswarmi and Sen (2014)\cite{GoswamiSen}.

\begin{figure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5d/5d_0-var-0.pdf}
	\caption{}
	\label{fig:neighbour1}
\end{subfigure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5d/5d_05-var-0.pdf}
	\caption{}
	\label{fig:neighbour2}
\end{subfigure}
\caption{The effect of different weights of propensity to trade with nearest neighbours, $\alpha$. Figure \ref{fig:neighbour1} is excludes saving ($\lambda = 0$), figure \ref{fig:neighbour2} includes saving ($\lambda = 0.5$).}
\label{fig:neighbour}
\end{figure}

Figure \ref{fig:neighbourpareto} shows the simulations for nearest neighbour interaction fitted to a Pareto distribution. The Pareto distribution should fit only for higher values of the wealth distribution, id est the tails of the distribution. Figure \ref{fig:neighbourpareto1} show that the power law fittings (Pareto distributions) appear to have similar shapes to the results from the simulations. One can see, however, that the data from the simulations tend drop quicker than their Pareto power law counterparts. Figure \ref{fig:neighourpareto2} shows a logarithmic version of figure \ref{fig:neighbourpareto1}. Here the Pareto fittings are straight lines, as one would assume, but the data from the simulations apparently inhibit more complexity than the a simple power law relationship between wealth and frequency.

\begin{figure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5d/5d_0-var-0-PARETO.pdf}
	\caption{}
	\label{fig:neighbourpareto1}
\end{subfigure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5d/5d_0-var-0-POWERLOG.pdf}
	\caption{}
	\label{fig:neighourpareto2}
\end{subfigure}
\caption{Power law fittings of neighbourhood effect wealth distributions. Figure \ref{fig:neighbourpareto1} is a linear plot, while figure \ref{fig:neighourpareto2} is double-logarithmic.}
\label{fig:neighbourpareto}
\end{figure}

%% Problem e

The last effect to consider is the former transaction effect, in combination with savings and nearest neighbour interactions. This effect is illustrated in figure \ref{fig:transbefore}. This figure is an attempt to replicate figure 5 in Goswami and Sen (2014)\cite{GoswamiSen}. Both subfigures show the wealth distribution for different values of $\gamma$ (propensity to trade with agents you have traded with before), but figure \ref{fig:transbefore1} weighs neighbour interactions less strongly than figure \ref{fig:transbefore2}, with $\alpha=1.0$ and $\alpha=2.0$ respectively.

\begin{figure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5e/5e_05-10-var.pdf}
	\caption{}
	\label{fig:transbefore1}
\end{subfigure}
\begin{subfigure}{.49\textwidth}
	\centering
	\includegraphics[width=\linewidth]{../figures/5e/5e_05-20-var.pdf}
	\caption{}
	\label{fig:transbefore2}
\end{subfigure}
\caption{Wealth distributions when weighing of previous transactions, in addition, has been taken into account. Figure \ref{fig:transbefore1} weighs wealth similarity less strongly ($\alpha=1$) than figure \ref{fig:transbefore2} ($\alpha=2.0$).}
\label{fig:transbefore}
\end{figure}

Lastly, figure \ref{fig:transbeforefit} show a power law fitting of the wealth distributions first presented in figure \ref{fig:transbefore}. The figure both includes ($\lambda=0.5$) and excludes savings ($\lambda=0$). The plot is logarithmic and the Pareto power distribution is therefore presented as a straight line.

\begin{figure}
	\centering
	\includegraphics[width=0.6\textwidth]{../figures/5e/5e_var-2-var-POWERlog_FIXXED.png}
	\caption{Power law fitting of wealth distribution including savings, nearest neighbhour- and previous transaction effects. The plot is logarithim and both includes ($\alpha=0$) and excludes ($\alpha=0.5$) savings.}
	\label{fig:transbeforefit}
\end{figure}

@@

\section{Parametrization from Patriarca et al.}
\label{app:partriarca}
A corresponding exact solution of an income distributions for a generic value of $\lambda$ with $0<\lambda<1$ is provided in Patriarca et al.\cite{Patriarca}. Fir one employs the reduced variable
\begin{equation}
x = \frac{m}{\ev{m}}
\end{equation}
the agent money in units of average money $\ev{m}$ and the parameter
\begin{equation}
n(\lambda) = 1 + \frac{3\lambda}{1-\lambda}.
\end{equation}
The money distributions, for arbitrary values of $\lambda$, are well fitted by the function
\begin{equation}
P_n(x) = a_nx^{n-1}e^{-nx}
\end{equation}
where $a_n$ is a normalization factor shown to be
\begin{equation}
a_n = \frac{n^n}{\Gamma(n)}
\end{equation}
\end{appendices}
